Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-08 Paper/paper.tex
Fixing abstract
Adding exit arrows to diagram
Starting to relabel states for demand

\begin{abstract}
Hospital throughput is often studied and optimised in isolation, ignoring the interactions between hospitals.
In this paper Critical Care Unit (CCU) interaction is placed within a game theoretic framework.
The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
A theoretical result is given that ensures the existence of a Nash Equilibrium.

@@

\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}
\node (A) at (0,0) [draw] {RG};
\node (B) at (2,0) [draw] {NH};
\draw [->] (-1,0) -- (A);
\draw [->] (3,0) -- (B);
\draw [->] (-1,0) -- ($(A)+(-.5,0)$) -- ($(A)+(-.5,.5)$) -- ($(A)+(.5,.5)$) -- ($(A)+(.5,.1)$) -- ($(B)+(-.4,.1)$);
\draw [->] (3,0) -- ($(B)+(.5,0)$) -- ($(B)+(.5,-.5)$) -- ($(B)+(-.5,-.5)$) -- ($(B)+(-.5,-.1)$) -- ($(A)+(.4,-.1)$);
\draw [->] (3,0) -- (B);
\node at ($(A) + (0,.8)$) {Divert?};
\node at ($(B) + (0,-.8)$) {Divert?};
\end{tikzpicture}
\caption{Diagrammatic representation of CCU interaction through patient diversion.}\label{diagramofdiversion}
\end{center}
\end{figure}

@@

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{a, b, c, d\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.

>>>>

\begin{abstract}
Hospital throughput is often studied and optimised in isolation, ignoring the interactions between hospitals.
In this paper Critical Care Unit (CCU) interaction is placed within a game theoretic framework.
The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
A theorem is given that proves that a Nash Equilibrium exists in pure strategies for the games considered.

@@

\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}
\node (A) at (0,0) [draw] {RG};
\node (B) at (2,0) [draw] {NH};
\draw [->] (-1,0) -- (A);
\draw [->] (3,0) -- (B);
\draw [->] (-1,0) -- ($(A)+(-.5,0)$) -- ($(A)+(-.5,.5)$) -- ($(A)+(.5,.5)$) -- ($(A)+(.5,.1)$) -- ($(B)+(-.4,.1)$);
\draw [->] (3,0) -- ($(B)+(.5,0)$) -- ($(B)+(.5,-.5)$) -- ($(B)+(-.5,-.5)$) -- ($(B)+(-.5,-.1)$) -- ($(A)+(.4,-.1)$);
\draw [->] (3,0) -- (B);
\node at ($(A) + (0,.8)$) {Divert?};
\node at ($(B) + (0,-.8)$) {Divert?};
\draw [->] (A) -- ($(A)+(0,-.5)$);
\draw [->] (B) -- ($(B)+(0,.5)$);
\end{tikzpicture}
\caption{Diagrammatic representation of CCU interaction through patient diversion.}\label{diagramofdiversion}
\end{center}
\end{figure}

@@

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.
